---
title: "cm015-oct24"
author: "Melanie Ang"
date: '2017-10-24'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R for strings

```{r}
my_string <- "Surrounded by quotes.' you can even put single quotes within "
my_string <- 'hello "hey" you can use double quotes within by starting with single quote'
my_string <- 'hello \'or put a back slash if you want to use quote within'
my_string <- "A slash \ "   # this doesn't show up
my_string <- "A slash \\ "  # but if you put a double slash

# Homework: how do you put a single slash in a string?
my_string <- "A slash '\\' "


```

```{r}
devtools::install_github("joeybernhardt/singer")
library(singer)
places <- unique(singer_locations$city)
```

## Tools of the trade

```{r}
devtools::install_github("tidyverse/glue")
library(tidyverse)
library(stringr)
library(glue)
```

glue and paste

```{r}
my_name <- "Mel"
age <- 26
colour <- "red"

# glue and paste, same purpose. glue easier to read
glue("My name is {my_name}. My age two years ago was {age - 2}.") 
paste0("My name is ",my_name,". My age two years ago was " ,age - 2) # commas surrounding obj
```

indentation - preserves indentation

```{r}
glue("
     My name is 
     {my_name}.
     My age two years ago was {age - 2}.")
```

## Challenge

Phrase: Today is Wednesday, October 24, 2017 and the sun shines

use: Sys.Date()
glue

```{r}
Sys.Date()

phrase <- glue("Today is {Sys.Date()} and the sun shines")
phrase <- glue("Today is {Today_date} and the sun shines",
               Today_date = Sys.Date())
```

```{r}
phrase <- "Today is {Today_date} and the sun shines"
phrase <- glue(phrase, Today_date = format(Sys.Date(), "%A, %B %d, %Y"))
?format
?Sys.Date
```

`glue_data` - to glue data frames together, recognizes the variables in the data frames

```{r}

singer_locations %>%
  glue_data("{artist_name} is from {city}.") %>%
  head()
```

Stringr package

```{r}
?getNamespaceExports

# provides all the functions produce from the package
getNamespaceExports("stringr") %>% 
  str_view("str_") # finds all string that displays a certain pattern aka anything that starts with str_
```

```{r}
getNamespaceExports("stringr") %>%
  str_subset("str_") $
```

### Challenge
Stringr is good for cleaning data frames

```{r}
places <- unique(singer_locations$city)
```

And, lets get all the places containing the strog "york"

```{r}
places %>%
  str_subset("york")

places %>%
  str_subset("York")

places %>%
  str_to_lower() %>% # change everything to lower case and search
  str_subset("york") # but this loses the ability to tell if its upper or lower


```

Regular expressions

```{r}
places %>%
  str_subset("[Yyb]ork") # this will search both upper, lower case y and bork and provide it

places %>%
  str_subset(coll("york", ignore_case = TRUE)) # not considering the case

places %>%
  str_subset("York$") # for all yorks that ends a string
```


```{r}
"[:digit:]"

# * means 0, 1 or more
places %>%
  str_subset("B.a*")
```


```{r}
test_string <- "hello "
test_string_2 <- " hello"
test_string_3 <- " hey hello "

?trimws # base r
?trim # glue package

trim(test_string_3) 
# this will remove beginning and trailing spaces from a character


# but what about from a data frame - does it still remove beg and trailing in a data frame?
colours <- c("red ", " navy blue ", " yellow")
numbers <- c(1 , 2, 3)
my_data_frame <- data.frame(colours, numbers)

my_data_frame %>%
  trim(my_data_frame$colours)

my_data_frame$colours %>%
  str_subset(" $")

my_data_frame$colours %>%
  str_subset("$ ")

as.data.frame(lapply(my_data_frame, trimws), stringsAsFactors = TRUE)
```

