---
title: "cm104-Nov2"
author: "Melanie Ang"
date: '2017-11-02'
output: html_document
---
In this class we look at list and nested list (a list within a list within a list). We look at how we can view list, how to extract elements within a list and how to manipulate elements etc using purrr

# Nested list
```{r load packages}
library(repurrrsive)
library(purrr)
library(tidyverse)
library(listviewer) # old versions of rstudio
```

List are different from data frames because they could have different structures within.

```{r}
str(gh_repos)
data("gh_repos")
gh_repos[[1]] # before you run this line, it is a promise aka rstudio has not download it

# View list
View(gh_users) # this doesn't work with older versions of Rstudio
jsonedit(gh_users) # but you can use jsonedit
```

extract information from lists: full name of first repo

```{r}
jsonedit(gh_repos)

gh_repos %>%
  map_chr(list(2, "name"))

gh_repos %>%
  map_chr(list(1, "full_name"))

gh_repos %>%
  map_chr(c(1, 3)) # same as before
```

Extract owner ID of fourth repo for each user
```{r}

# use int if the fnal extract is integer
gh_repos %>%
  map_int(list(4, "owner", "id")) %>%
  map_int(list("id"))

#c(2,2), magrittr::extract, "full_name")

# gh_repos[2,2]
```

Convert list to data frames - using enframe()
```{r}
library(tibble) # building a list

u_id <- gh_repos %>%
  map_int(list(1,"owner", "id"))

str(gh_repos, max.level = 1) 
# do not go through the full structure, stop at level 1
# but this has no names, so hard to identify the rows

# set names for each list, because each id is representative of each repo
gh_repos_named <- gh_repos %>%
  set_names(u_id)

# only display level 1 after naming
str(gh_repos_named, max.level = 1) 

# rename column - name of list and the remainder of list stuff
gh_repos_df <- gh_repos_named %>%
  enframe("user_id", "repo_stuff")
jsonedit(gh_repos_df)
```

Create an enframe df of repos with rownames being their login

```{r}
# View the list
jsonedit(gh_repos)

# Extract the login info from each repo and assign it
u_login <- gh_repos %>%
  map_chr(list(1, "owner", "login"))

# Display the level 1 as a base line
str(gh_repos, max.level = 1)

# Name the row with the login
u_login_named <- gh_repos %>%
  set_names(u_login)

# Display it at level 1 to see if it works
str(u_login_named, max.level = 1)

# Create it as a data frame
gh_repos_login_df <- u_login_named %>%
  enframe("login_name", "repo_things")

gh_repos_login_df %>%
  filter(login_name %in% c("masalmon")) %>%
  mutate(number_of_repo = map_int(repo_things, length)) 
# mapping within repo_things and finding length
# mutate(number_of_repo = length(repo_things)) - wrong because it will just look at new frame, there is 1 repo in this data frame
```

GAME OF THRONES EXAMPLE - 4 examples for performing manipulations within a list
?got_chars
```{r}
jsonedit(got_chars)
map(got_chars, "aliases")

aliases_named <- set_names(map(got_chars, "aliases"),
    map(got_chars, "name"))


# Use length to find number of elements, use map to find how many within.. it goes within a list and find info depending on function
length(aliases_named)

map_int(aliases_named, length) # instead of length you can also create your own function

# create function
collapse_by_comma <- function(vec_of_string){
  paste(vec_of_string, collapse = ",")
}

# test function
collapse_by_comma(c("first","second"))

# map goes within and collapse with comma
map(aliases_named, collapse_by_comma) 

# You could also build the function within here <-
map(aliases_named,
    function(v_o_c) paste(v_o_c, collapse = ","))

# if you use one argument before .x will represent that
map(aliases_named, ~paste(.x, collapse = ","))

```
